## Features for Training data

We are going to use the molecular docking results form 1% of the library to train the LighGBM algorithm. First we need to combine the features we extracted in the previous step with the results form the molecular docking of the 1%. To do this you have two options. 

### Option 1: Combine the data frames

The first option is to combine the data frames. If you are working with very large feature matrix, we highly recomend using [`Option 2`](#option-2-use-the-pcaprop-function).

```{r}
first_docking <- read.csv("./data/first_docking.csv")
features <- read.csv("data/Tetra_prop_n.csv")

first_docking <- dplyr::left_join(first_docking, features, by = c("Title" = "Y"))

```

### Option 2: Use the PCAprop function

PCAprop function described before cna also take a custom list of peptides. 

```{r}
first_docking <- read.csv("./data/first_docking.csv")

first_features <- PCAprop(n = 4, custom.list = T, PeList = first_docking$Title, norm = T)

first_docking <- dplyr::left_join(first_docking, first_features, by = c("Title" = "Sequence"))
```

